\cvsection{Experience}
\begin{cventries}
  
  \cventry
    {HPC (High performance Computing )}
    {CADS (Centro de Análisis de Datos y Supercomputo)}
    {Universidad de Guadalajara (UDG)}
    {September 2018 - Still working here}
    {
      \begin{cvitems}
        \item {I'm work with a cluster hpc from 1 year ago.This cluster its of udg with  name Leo Atrox and OS RHEL.}
        \item {I'm create a specific environments to investigator, this environment it is created based on the requests of the investigator,the software is compiled to the cluster.}
        \item {This cluster controls the work with slurm.}
      \end{cvitems}
    }

	\cventry
	{Specially Centos, RHEL, Ubuntu and Debian}
	{Knowledge in Unix Linux \& user environment control}
	{I like to lern about linux }
	{Since January 2017 }
	{
	\begin{cvitems}
		\item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
		\item {Improved functionality on military command and control system for incident response with Java Servlet.}
		\item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
	\end{cvitems}
}
  \cventry
    {Creation of test environments with virtual machines}
    {VMware ESXi }
    {Pohang, S.Korea}
    {Sep. 2012 - Feb. 2013}
    {
      \begin{cvitems}
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems} 
    }
  \cventry
    {Virtual Enviroments}
    {Docker}
    {December 2018}
    {I'm still learning}
    {
      \begin{cvitems}
        \item {I'm creating a specifics containers for a users, this containers make with a special software and configurations for users request, to create test environments quickly and efficiently.
        \item Also I'm creating a environments in a containers for introduce new usersto SO linux.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {OpenHPC}
    {Seoul, S.Korea}
    {Dec. 2011 - Feb. 2012}
    {
      \begin{cvitems}
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    
\end{cventries}
